Specifying and Verifying the Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
Make contributions less verbose

In this paper, we make the following contributions:
%
\begin{itemize}
\item We introduce our specification language for stencils
  that captures many common forms of data access pattern
  (\S~\ref{sec:lang});

@@

\item We report on a quantitative study of stencil computations on a
  corpus of numerical Fortran programs (ranging from small to large)
  (\S~\ref{sec:evaluation}), totalling one million lines of code. Our tool
  identifies and infers specifications for 35,000 stencil computations in the
  corpus. Approximately 10\% of the stencils we found are non-trivial,
  corresponding to code which is a possible source of errors. This validates
  our hypothesis that the majority of stencil computations have a regular
  shape, and validates the design of our language in its capability to capture
  many core patterns.

\item We give a detailed verification case study of two
  particular stencil computations commonly used in scientifc computing,
  simulating programming errors. Our approach is able to detect all
  possible indexing errors for these computations.
\end{itemize}
%

>>>>

In this paper, we make the following contributions:
%
\begin{itemize}
\item We introduce a specification language for stencils
  that captures common forms of data access patterns
  (\S~\ref{sec:lang});

@@

\item We report on a quantitative study of stencil computations on a
  corpus of numerical Fortran program
  (\S~\ref{sec:evaluation}), totalling one million lines of code. Our tool
  identifies and infers specifications for 35,000 stencil computations in the
  corpus. Approximately 10\% of the stencils we found are non-trivial,
  corresponding to code which is a possible source of errors. This validates
  our hypothesis that the majority of stencil computations have a regular
  shape, and validates the design of our language in its capability to capture
  many core patterns.

\item We give a detailed verification case study of two
  stencil computations commonly used in scientifc computing,
  simulating programming errors. Our approach detects all
  possible indexing errors for these computations.
\end{itemize}
%
